Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
saved

The domains are constructed to challenge planners to perform
better. This creates issues when comparing the domains to their real-world match as can be easily seen 
in the \textsc{Traffic} domain.

@@

The traffic domain describes a crossroad with traffic lights, modelled as
cells. Either the north to south road has a green light, the west to east road
or all lights are red. The model uses a finite state machine that handles the
lights so that the lights are never green at the same time. This would be the
only dangerous situation on the crossroad. The difficulty in this domain is
the number of states, which grows exponentially with the number of cells.
Besides that it is an uninteresting probabilistic problem because it does
not satisfy the probabilistic interesting test.

The UAV domain has a resemblance of the Navigation domain. Both are goal
oriented and have to navigate something (either the robot itself, or a data
package) from an initial state to a goal. Also after each step a dead end can
be reached, the robot disappears or the data package is not delivered.
The probability this happens is static in the navigation domain, but dependent
on the neighbors in the UAV domain. This variable probability has a resemblance
of the SysAdmin domain, where the probability that a server shuts down is also
dependent on the neighbors.

>>>>

The domains are constructed to challenge planners to perform
better. This creates issues when comparing the domains to their real-world match as can be easily seen 
in the \textsc{Traffic} domain. Although the current domain contains no dead-ends and is thus probabilistically
uninteresting, it will gain probabilistic interestingness by introducing the uncertain behavior of drivers and failure
of the lighting system. If so, the performance of FF-Replan will be strongly decreased, whilst \textsc{Gourmand} will keep its anytime performance.

@@

The UAV domain has some resemblance with the \textsc{Navigation} domain. Both are goal
oriented and have to navigate something (either the robot itself, or a data
package) from an initial state to a goal. After each step a dead end can
be reached where the robot disappears or the data package is not delivered.
Although the probability of disappearing is static in the \textsc{Navigation} domain, the probability is dependent of the 
amount of neighbors and distance in the UAV domain. This variable probability has a resemblance
of the SysAdmin domain, where the probability that a server shuts down is also
dependent on the neighbors.
